\documentclass[10pt,letterpaper]{article}

\usepackage[left=0.45in,right=0.45in,top=0.55in,bottom=0.55in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[scale=0.96]{tgheros}
\renewcommand{\familydefault}{\sfdefault}
\usepackage[final,protrusion=true,expansion=false]{microtype}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage[dvipsnames]{xcolor}

\definecolor{accent}{HTML}{1F4E5F}
\definecolor{textgray}{HTML}{303030}
\definecolor{muted}{HTML}{5E6A6E}

\hypersetup{
  colorlinks=true,
  urlcolor=accent,
  linkcolor=accent
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
\setlength{\emergencystretch}{2em}
\linespread{1.08}
\setlist[itemize]{leftmargin=0.16in,itemsep=3pt,topsep=4pt,parsep=1pt,partopsep=0pt}
\setlist[enumerate]{leftmargin=0.24in,itemsep=5pt,topsep=4pt,parsep=1pt,partopsep=0pt}
\titleformat{\section}
  {\large\bfseries\color{accent}}
  {}
  {0pt}
  {}
  [\vspace{-1pt}{\color{accent}\titlerule[0.65pt]}]
\titlespacing*{\section}{0pt}{9pt}{6pt}

\newcommand{\resumeSubheading}[4]{%
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    {\large\textbf{#1}} & {\small\color{muted} #2} \\
    {\small\textit{#3}} & {\small\textit{\color{muted} #4}}
  \end{tabular*}\vspace{-2pt}
}
\newcommand{\educationEntry}[3]{%
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & {\small\color{muted} #2} \\
    \small #3 &
  \end{tabular*}\vspace{2pt}
}
\newcommand{\resumeItem}[1]{\item \small #1}
\newcommand{\resumeNamedItem}[2]{\item \small \textbf{\color{accent} #1:} #2}
\newcommand{\pubitem}[3]{%
  \item \small {\color{accent}\textbf{#1}} \quad \textit{#2}\\[-1pt]
  {\color{textgray}#3}
}

\begin{document}
\color{textgray}

\begin{center}
  {\fontsize{22}{24}\selectfont \textbf{\color{accent} Navid Rezazadeh}}\\[3pt]
  \small Machine Learning Research \textbar{} AI Research \textbar{} Generative Models, LLMs, and Scientific Computing\\[3pt]
  \href{mailto:nrezazad@uci.edu}{nrezazad@uci.edu} \textbar{}
  +1 (573) 465-4854 \textbar{}
  \href{https://linkedin.com/in/nrezazadeh}{linkedin.com/in/nrezazadeh} \textbar{}
  \href{https://github.com/navidrezazad}{github.com/navidrezazad} \textbar{}
  \href{https://tinyurl.com/NavidScholar}{Google Scholar}
\end{center}
\vspace{-6pt}

\section{Summary}
\small Machine learning research engineer at Apple. ICML 2026 spotlight on LLM decoding; recent arXiv work on transformer verification (Vertex-Softmax); in-progress work on LLM reasoning dynamics. Research spans LLM robustness, generative modeling, time-series learning, and GPU-accelerated scientific computing.

\section{Experience}
\resumeSubheading{Apple}{San Diego, CA}{Machine Learning Research Engineer}{Jun 2022 -- Present}
\begin{itemize}
  \resumeNamedItem{Vertex-Softmax}{Developed an exact softmax-optimization primitive with log-linear complexity that produces the tightest possible bounds from pre-softmax score intervals; integrated into a CROWN-style verifier, it improves certified rates and outperforms $\alpha$-CROWN and branch-and-bound on MNIST, Fashion-MNIST, and CIFAR-10 attention models. \href{https://arxiv.org/abs/2605.10974}{arXiv:2605.10974}, code at \href{https://github.com/navidrezazad/VertexSoftmax}{github.com/navidrezazad/VertexSoftmax}.}
  \resumeNamedItem{Geometry-Aware Decoding}{Co-developed a geometry-aware LLM decoding algorithm combining Wasserstein-regularized truncation with mass penalties to produce more reliable generation; ICML 2026 spotlight.}
  \resumeNamedItem{Backtracking Dynamics}{Investigated backtracking bursts in long reasoning traces of LLMs and proposed early-exit criteria for efficient generation.}
  \resumeNamedItem{Transformer Forecasting}{Designed transformer and Informer-based architectures for short-horizon forecasting on high-resolution time-series signals, benchmarked against ARIMA/ARMA statistical baselines under rolling out-of-sample validation.}
  \resumeNamedItem{Generative Modeling}{Built GAN, diffusion, and copula-based generative workflows for scientific simulator surrogates; validated samples with MMD, feature statistics, and chi-square distributional tests.}
  \resumeNamedItem{GPU Scientific Computing}{Re-architected scalar scientific pipelines into batched PyTorch/CUDA with multi-GPU data parallelism, reducing per-run evaluation from multi-week scale to sub-hour while preserving CPU-reference parity.}
\end{itemize}

\resumeSubheading{University of California, Irvine}{Irvine, CA}{Graduate Research Assistant}{Jun 2016 -- Jun 2022}
\begin{itemize}
  \resumeNamedItem{Learning for Control}{Jointly learned a neural control policy and its contraction metric from offline trajectory data, enforcing stability guarantees via contraction theory; NeurIPS SafeRL Best Paper (IEEE RA-L 2022).}
  \resumeNamedItem{Probabilistic Estimation}{Built Kalman, sigma-point, and particle filtering methods for probabilistic localization and state estimation in noisy networked systems.}
  \resumeNamedItem{Distributed Optimization}{Developed distributed algorithms for multi-agent submodular maximization and persistent monitoring with provable optimality bounds, using multilinear extensions, stochastic Pipage rounding, and receding-horizon policy design; extended to privacy-aware settings with a stochastic rounding scheme that explicitly trades optimality for per-agent privacy guarantees (Automatica 2023, Automatica 2021, IEEE CDC 2022).}
  \resumeNamedItem{Private Networked Systems}{Designed additive-obfuscation privacy-preserving consensus protocols with formal deterministic privacy guarantees against network eavesdroppers while preserving convergence to the true average (IEEE TCNS 2024).}
\end{itemize}

\section{Education}
\educationEntry{University of California, Irvine}{2017 -- 2022}{Ph.D. Mechanical \& Aerospace Engineering, GPA 3.99/4.00}
\small \textit{Thesis: Distributed Strategy Selection Over Graphs: Optimality and Privacy}\vspace{2pt}

\educationEntry{University of California, Irvine}{2016 -- 2017}{M.S. Mechanical \& Aerospace Engineering, GPA 4.00/4.00}
\educationEntry{Sharif University of Technology}{2010 -- 2014}{B.S. Mechanical Engineering, GPA 3.85/4.00}
\small
\textbf{\color{accent} Selected Coursework}\\
\textbf{\color{accent} Mathematics:} Real Analysis; Advanced Calculus; Linear Algebra; Optimal Control.\\
\textbf{\color{accent} Probability \& Statistics:} Stochastic Processes; Bayesian Data Analysis; Advanced Estimation and Detection; Classification, Parameter Estimation, and Filtering; Probabilistic Learning.\\
\textbf{\color{accent} ML \& Optimization:} Deep Learning and Sequence Models; Convex Optimization; Advanced Optimization Methods; Algorithms.

\section{Core Technical Skills}
\small
\textbf{\color{accent} ML/AI:} LLM decoding, transformer verification, sequence models, generative models (GANs, diffusion, copulas), simulator surrogates, time-series learning, calibration, model validation.\\
\textbf{\color{accent} Mathematics:} Optimization, stochastic processes, graph algorithms, control and estimation, linear algebra, Monte Carlo methods.\\
\textbf{\color{accent} Tools \& Frameworks:} Python, PyTorch, CUDA, multi-GPU training, NumPy, C/C++, Git.

\section{Publications and Manuscripts}
\begin{enumerate}[label={[\arabic*]},itemsep=6pt,topsep=4pt]
  \pubitem{\href{https://arxiv.org/abs/2605.10974}{arXiv:2605.10974}}{Vertex-Softmax: Tight Transformer Verification via Exact Softmax Optimization.}{\textbf{N. Rezazadeh} and A. Gholami Davoodi.}
  \pubitem{Under preparation}{The Shape of Overthinking: Backtracking Bursts in Long Reasoning Traces.}{\textbf{N. Rezazadeh} and A. Gholami.}
  \pubitem{ICML 2026 (spotlight)}{Geometry-Aware Decoding with Wasserstein-Regularized Truncation and Mass Penalties for LLMs.}{A. Gholami Davoodi, \textbf{N. Rezazadeh}, S.\ P. Mousavi Davoudi, and P. Pezeshkpour.}
  \pubitem{IEEE RA-L, 2022; NeurIPS SafeRL Best Paper Award}{Learning Contraction Policies From Offline Data.}{\textbf{N. Rezazadeh}, M. Kolarich, S.\ S. Kia, and N. Mehr.}
  \pubitem{IEEE TCNS, 2024}{A Study of Privacy Preservation in Average Consensus Algorithm via Deterministic Obfuscation Signals.}{\textbf{N. Rezazadeh} and S.\ S. Kia.}
  \pubitem{Automatica, 2023}{Distributed Strategy Selection: A Submodular Set Function Maximization Approach.}{\textbf{N. Rezazadeh} and S.\ S. Kia.}
  \pubitem{IEEE CDC, 2022}{Distributed Submodular Maximization: Trading Performance for Privacy.}{\textbf{N. Rezazadeh} and S.\ S. Kia.}
  \pubitem{Automatica, 2021}{A Sub-Modular Receding Horizon Solution for Mobile Multi-Agent Persistent Monitoring.}{\textbf{N. Rezazadeh} and S.\ S. Kia.}
  \pubitem{IEEE CDC, 2021}{Multi-Agent Maximization of a Monotone Submodular Function via Maximum Consensus.}{\textbf{N. Rezazadeh} and S.\ S. Kia.}
  \pubitem{IFAC-PapersOnLine, 2019}{A Sub-Modular Receding Horizon Approach to Persistent Monitoring for a Group of Mobile Agents Over an Urban Area.}{\textbf{N. Rezazadeh} and S.\ S. Kia.}
  \pubitem{arXiv, 2019}{Privacy Preservation in Continuous-Time Average Consensus Algorithm via Deterministic Additive Obfuscation Signals.}{\textbf{N. Rezazadeh} and S.\ S. Kia.}
  \pubitem{ACC, 2018}{Privacy Preservation in a Continuous-Time Static Average Consensus Algorithm Over Directed Graphs.}{\textbf{N. Rezazadeh} and S.\ S. Kia.}
\end{enumerate}

\section{Honors}
\begin{itemize}
  \resumeItem{NeurIPS SafeRL Best Paper Award}
  \resumeItem{Holmes Fellowship, UCI MAE}
  \resumeItem{Samueli Endowed Fellowship, UCI}
  \resumeItem{Semifinalist, Iran National Physics and Mathematics Olympiads}
  \resumeItem{Ranked 250th among 300{,}000+ in Iran national university entrance exam}
\end{itemize}

\end{document}
